\Large Analyzing the Supreme Court Citation Network

### 2017-12-02 Tex/paper.tex
updating theory section

Mutuality:

\textbf{Also popularity} If j served as precedent for i, j is authoritative regarding the rule of i, and should also be cited.

>>>>

\textbf{Mutuality:} When deciding a set of related cases, the courts opinions regularly reference each other in order to reinforce their arguments...

On a more specific level, Western argues that flight engineers must meet the same stringent qualifications as pilots, and that it was therefore quite logical to extend to flight engineers the FAA's age 60 retirement rule for pilots. Although the FAA's rule for pilots, adopted for safety reasons, is relevant evidence in the airline's BFOQ defense, it is not to be accorded conclusive weight. Johnson v. Mayor and City Council of Baltimore, ante at 472 U. S. 370-371. The extent to which the rule is probative varies with the weight of the evidence supporting its safety rationale and "the congruity between the . . . occupations at issue." Ante at 472 U. S. 371. In this case, the evidence clearly established that the FAA, Western, and other airlines all recognized that the qualifications for a flight engineer were less rigorous than those required for a pilot. [Footnote 28]

https://supreme.justia.com/cases/federal/us/472/400/case.html

The city, supported by several amici, argues for affirmance nonetheless. It asserts first that the federal civil service statute is not just a federal retirement provision unrelated to the ADEA, but in fact establishes age as a BFOQ for federal firefighters based on factors that properly go into that determination under the ADEA, see Western Air Lines, Inc. v. Criswell, post p. 472 U. S. 400. Second, the city asserts, a congressional finding that age is a BFOQ for a certain occupation is dispositive of that determination with respect to nonfederal employees in that occupation. We consider each of these contentions in turn.

\url{https://supreme.justia.com/cases/federal/us/472/353/case.html#370}

\textbf{Also popularity} If j served as precedent for i, j is authoritative regarding the rule of i, and should also be cited. Citations beget citations. Citation confers authority. Cases are even discussed in opinions in terms of the extent of influence they have had on other cases,

"The first case in which this Court struck down a statute under the Equal Protection Clause of the Fourteenth Amendment was Strauder v. West Virginia, 100 U. S. 303, decided in the 1879 Term. [Footnote 2/1] In the 1961 Term, we squarely held that the manner of apportionment of members of a state legislature raised a justiciable question under the Equal Protection Clause, Baker v. Carr, 369 U. S. 186. That case was followed by numerous others, e.g.: that one person could not be given twice or 10 times the voting power of another person in a state-wide election merely because he lived in a rural area..."

https://supreme.justia.com/cases/federal/us/400/112/case.html
